Type-safe client-server communication for web applications

### 2014-02-28 paper.tex
Fix silly typo, label for Haste section.

\begin{itemize}
  \item Poor man's concurrency monad
  \item Conditional compilation
  \item Printf trick to turn export into [JSON] -> f
  \item JSON over WebSockets used for transport
  \item Server event loop awaits commands, dispatches functions, sends data back
  \item Client sends command with nonce and blocks on MVar, event loop fills
        MVar when return value with proper nonce arrives
  \item Throw away unused stuff on client
\end{itemize}

\section{The Haste compiler}

In order to allow the same language to be used on both client and server, we
obviously need some way to compile that language into Javascript. To this end,
we make use of the Haste compiler\ \cite{haste}, developed as a MSc thesis and
extended as part of this work. Haste builds on the GHC compiler to provide
the full Haskell language, including most GHC-specific extensions, in the
browser.

@@

The astute reader may notice that this is exactly what the \lstinline!export!
does as well, the difference being that \export!export! links the identifier to
the value it represents on the type level, making it impossible to call
non-existent remote functions and break the program's type safety in other ways.

@@

>>>>

\section{The Haste compiler}\label{sec:haste}

In order to allow the same language to be used on both client and server, we
obviously need some way to compile that language into Javascript. To this end,
we make use of the Haste compiler\ \cite{haste}, started as an MSc thesis and
continued as part of this work. Haste builds on the GHC compiler to provide
the full Haskell language, including most GHC-specific extensions, in the
browser.

@@

The astute reader may notice that this is exactly what the \lstinline!export!
does as well, the difference being that \lstinline!export! links the identifier
to the value it represents on the type level, making it impossible to call
non-existent remote functions and break the program's type safety in other ways.

@@

\bibitem[Claessen (1999)]{concurrencymonad}
K. Claessen: Functional Pearls: A poor man's concurrency monad, 1999
